---
title: "Reproducible Documents"
subtitle: "A hands-on tutorial for Stata users"
author:
  - Lars Vilhuber
date: today
format:
  html:
    toc: true
    code-overflow: wrap
    reference-location: document
---

```{r config,include=FALSE}
library(here)

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
if (GITHUB_REPOSITORY == "") GITHUB_REPOSITORY <- "larsvilhuber/reproducible-documents"
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])

# Numbers quoted in the text are computed, not typed (same regression as in the examples)
auto <- haven::read_dta("https://www.stata-press.com/data/r19/auto.dta")
AUTO_COEF_MPG <- sprintf("%.1f", coef(lm(price ~ mpg + weight, data = auto))["mpg"])
```

<!--
This is the article-length, textual companion to the slide deck in `presentation/`.
It follows the same structure. The step-by-step instructions are the README files
in examples/, included below, so that there is only one copy of them.
-->

# Introduction

> In our experiment, welfare increases by 2.3% under policy A, while it increases by 1.1% under policy B.

Where do these numbers come from? In most papers, someone ran the analysis,
looked at the output, and typed the numbers into the text. Over the course of a
paper's life, the analysis changes, and the numbers in the text are not always
updated. Data Editors find this often: numbers in the text that cannot be traced
to the code, or that no longer match it. The remedy is simple, in the words of
the JPE Data Editor: "never type a numeric result. Read it from disk"
([Oswald 2026](https://jpedataeditor.github.io/posts/20260910-latex-macros/)).

This tutorial walks through four ways to do that, from simple to more complex.
All four use the same data (Stata's `auto` dataset) and the same regression
(`regress price mpg weight`), so the same number, `r AUTO_COEF_MPG`, appears in all four
documents, and is never typed by hand (not even here).

| | You write | It runs on | You get |
|:--|:--|:--|:--|
| 1 | Quarto (Markdown + R) | posit.cloud (browser) | HTML, Word, PDF |
| 2 | Stata do-file + LaTeX | your laptop | PDF |
| 3 | Stata `dyndoc` (Markdown) | your laptop | Word |
| 4 | Jupyter notebook + Stata | Colab or Binder (browser) | Word, PDF |

You need a web browser, a free [posit.cloud](https://posit.cloud) account,
Stata 16 or later on your laptop, and your Stata license file (for part 4,
which runs on Google Colab with a Google account, or on Binder without one). To compile LaTeX without installing it, a free
[Overleaf](https://www.overleaf.com) account helps. The slides are at
<`r WEBSITE_URL`>, and all files are in <`r REPOSITORY_URL`>.

```{r, child=here::here("examples", "01-quarto-posit-cloud", "README.md")}
```

```{r, child=here::here("examples", "02-stata-latex-macros", "README.md")}
```

```{r, child=here::here("examples", "03-stata-dyndoc-word", "README.md")}
```

```{r, child=here::here("examples", "04-jupyter-colab", "README.md")}
```

# Which one should I use?

If you write your paper in LaTeX, let Stata write the numbers as LaTeX macros
(part 2). If you write in Word, Stata's `dyndoc` (part 3) or `putdocx` (part 4)
create the document for you. Jupyter notebooks (part 4) are good to explore, and
to show your work step by step. Quarto (part 1) creates HTML, Word, PDF, and
slides from one source. They can be combined: Stata writes the numbers, Quarto
writes the paper.

Whatever the tool, the ideas are the same:

- **One source of truth**: each number lives in exactly one place.
- **Never type a number**: the code puts it into the document.
- **Re-run everything**: from data to document, in one go.
- **Keep it all**: code, generated files, and documents go into your replication package.

## Learn more

- Quarto: <https://quarto.org/docs/get-started/>
- Stata `dyndoc`, `putdocx`, `putpdf`, `etable`: `help dyndoc` etc. in Stata, and the [Reporting manual](https://www.stata.com/manuals/rpt.pdf)
- PyStata (Stata in Jupyter): <https://www.stata.com/python/pystata19/>
- Oswald, Florian. 2026. "Are Your in-Text Numbers Correct? Do They Match Your Table?" JPE Data Editor Blog. <https://jpedataeditor.github.io/posts/20260910-latex-macros/>

```{r, child=c(here::here('99-links.md'))}
```
