---
title: "My First Reproducible Document"
author: "Your Name"
date: today
format:
  html:
    embed-resources: true
  docx: default
  typst: default
---

## About this document

This is a **Quarto** document. You write the text in *Markdown*, and you put
code into *chunks*. When you click **Render**, Quarto runs the code and puts
the numbers, tables, and figures into the document. No copy and paste!

The code is written in R, but every chunk shows the Stata command that does
the same thing.

## The data

```{r}
#| label: load-data
# Stata: sysuse auto, clear
library(haven)
auto <- read_dta("https://www.stata-press.com/data/r19/auto.dta")
```

We use the 1978 automobile data that ships with Stata. The data contain
`r nrow(auto)` cars, and the average price is `r round(mean(auto$price))`
dollars.

## Summary statistics

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary statistics"
# Stata: summarize price mpg weight
vars <- c("price", "mpg", "weight")
stats <- data.frame(
  Variable = vars,
  Mean = sapply(auto[vars], mean),
  SD   = sapply(auto[vars], sd),
  Min  = sapply(auto[vars], min),
  Max  = sapply(auto[vars], max)
)
knitr::kable(stats, digits = 1, row.names = FALSE)
```

## A regression

```{r}
#| label: tbl-regression
#| tbl-cap: "Regression of price on mileage and weight"
# Stata: regress price mpg weight
model <- lm(price ~ mpg + weight, data = auto)
knitr::kable(summary(model)$coefficients, digits = 2)
```

Holding weight constant, one more mile per gallon changes the price by
`r round(coef(model)["mpg"], 1)` dollars (@tbl-regression).

## A figure

```{r}
#| label: fig-scatter
#| fig-cap: "Price and fuel efficiency"
# Stata: twoway (scatter price mpg) (lfit price mpg)
plot(auto$mpg, auto$price, xlab = "Mileage (mpg)", ylab = "Price (USD)")
abline(lm(price ~ mpg, data = auto))
```
